Measuring Software Ticket Quality using Statistical Analysis

### 2018-04-17 paper/paper.tex
Include flow figure and start completing the data set section

This \LaTeX template is based on the ACM \texttt{sig-alternate} class.
The layout is two-column text. Generally figures and tables only
extend to one column width, e.g.\ Table \ref{tab-eg},
but it is possible to make them
stretch over both columns using the \texttt{figure*} and
\texttt{table*} environments. For an example, see Figure \ref{fig-eg}.

@@

Again, Simon Peyton Jones has a lovely description of how to write a
paper on his
website.
Personally, I put URLs in footnotes and \emph{bona fide} references
in the bibliography. For instance, Turing \cite{turing37computable}
and Knuth \cite{knuth68art} would not be out of place in list of
references.
How many references? Hard to say. Five is not enough, 50 is pushing
it.

\subsection{User Interface}

Blah blah blah
Blah blah blah
Blah blah blah
Blah blah blah

% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{Foo}

Blah blah blah
Blah blah blah
Blah blah blah

\subsubsection{Bar}
\textsf{Blah} \textit{blah} \textbf{blah}

@@

Graphs are always good. I recommend getting to grips with Matlab, R or
gnuplot rather than exporting horribly Excel bitmapped graphs.

>>>>

@@

\begin{figure*}
\begin{center}
\includegraphics[scale=0.3]{images/flow.png}
\end{center}
\caption{\label{fig-eg}Flow of the whole application.}
\end{figure*}

The first step to building the data set was to create a tool that was able to execute all the commands that we required:
fetching the tickets from any Jira instance, storing them into some form of database, analyze the variables of interest, 
automatically plot the correlations between them and run statistical analysis on the data. After careful consideration, 
we decided that Go was the best way to go for various reasons:
  \begin{itemize}
    \item it is designed with simplicity in min, thus making it easier for others who might join the project to read 
    and understand the codebase;
    \item it is compiled, statically typed, which implies that it is a much faster candidate than other interpreted languages
    such as Ruby or Python;
    \item is is designed with concurrency in mind, thus it helps reduce times of execution and computing power considerably;
  \end{itemize}

Figure \ref{} The following two subsections will describe in detail how the process of building the data set was undergone.

\subsection{Fetch and Store}

This is the first command implemented in our tool - it is desgined to fetch, from any valid Jira URL, any number of tickets 
and then store everything inside an instance of BoltDB \cite{bolt}, which is a very simple yet powerful key-value pair 
database. The whole process is parallelized with the possibility of scaling even up to hundreds of goroutines
(i.e. lightweight threads) running concurrently.

In terms of projects selected, we have opted for the Apache Software Foundation which open-sourced some of the most popular
software applications. Moreover, they have all their projects' issue tracking systems hosted on Jira, thus we could also 
achieve consistency easier.

\subsection{Analyse}

@@

\subsection{Attachments}

\subsection{Comments}

\subsection{Summary and Description}

\subsection{Grammar Correctness}

\subsection{Sentiment Analysis}

\subsection{Steps to Reproduce}

\subsection{Stack Traces}
